My first special thanks goes, of course, to my mentors: Peter Pickl from Tübingen (I would write the title "Prof. Dr.", but I suspect he would feel this as putting distance between us) and Assoc. Prof. Michele Coghi from Trento.
Peter was always available, kind and patient regardless of how many times I did not understand a concept, or how long was a document which I sent for corrections.
Together with this he was usually ten steps ahead when he guessed what the final outcome of a mathematical question was, and he was incredibly skilled in visualizing and communicating the intuitions he had about such a problem.
The combination of these characteristics made of him by far the best lead I could have had to complete this work.
Furthermore I will be eternally grateful to Assoc. Prof. Coghi because not only he crafted the all-encompassing amazing course on which I built my initial knowledge on SDEs, but he also was kind enough to accept the role of mentor from Trento.

I also really need to thank the professors and the staff of the offices who patiently helped me managing the documents needed to obtain this double degree and have the many exams recognized in both the institutions of Trento and Tübingen.
In particular a pivotal role was played by the Prof. Willem Adriaan De Graaf, the Jun.-Prof. Daniele Agostini and the secretary from the international mobility office of the science and technology area of Trento, Vanina Micheletti.

An enormous special thanks goes to the person that supported me all my life in every imaginable way (and this journey was no exception), namely my father Paolo Lanzi.
Besides having a big, enormous, gigantic heart, he always offered wise pieces of advice to approach my life in a very optimistic, positive and pragmatic way, words of wisdom which I admit I should more often listen to.

I also owe a lot to my partner Beáta Harmati, who all this time supported me and bore not only all my quirks, but also all the weight of this work.
She did not complain when, inspired, I wrote 10 hours straight from dusk till dawn, and the day after she asked if I enjoyed the creative process.
She did not groan when at the last minute I declined to attend an event to stay at home and try a new idea which came to my mind. 
She instead cheered me up if I could not shout "Eureka!" and shared my joy if instead I had a small breakthrough, and in general made everything she could to make my days feel lighter.

Finally I want to thank all the colleagues and friends: they made my days better, listened to me speaking day and night about amoebas and their chemical shouting, gave me good pieces of advice to reach my goals, to organize and present my ideas and recommended me tons of inspiring materials.
Besides, they gave me their feedback about the way I presented different parts of my work.
And shaved my head blindfolded when I asked them to.
Among these people are notable: 
\begin{itemize}
	\item Each single one of the sparkling big heads from the research group of the fourth floor of the mathematics department of Tübingen, in particular the students whom with I share the office: Cedric Igelspacher, {\malayalamfont റാഷി കൈമൾ}/Rashi Kaimal, Jorge Acuña-Flores, Luca Damian.
	\item The crew from the almost-all-physics group Tüber-Party (Beáta Harmati, Μιχαήλ Κυριαζής/Michail Kiriazis, Anurag Sharma, Gregor Scholz and {\malayalamfont ജിബിൻ തോമസ്}/Jibin Thomas).
	\item The countless powerful brains who took interest in my work when I explained it and who shared inspiring ideas about it, namely Manuel Lubetzi, Nele Dierlamm, Elias Mennad, Matej Jazbec, Γεώργιος Βρετινάρης/Georgios Vretinaris, Edoardo Tesei, Javier Colominas, Georg Reich, Gabriele Perini and many others.
	\item The people whom I worked with before focusing full-time on this master's thesis, most notably my amazing ex-boss Thomas Jarosch and my coworkers Adrian, Kristóf, Christian, Kejdi, and many others.
	\item The group of mathematicians who I met through the Rom Seminar, among which I can list Prof. Rainer Nagel, Prof. Dr. Stefan Teufel, Prof. Dr. Ulrich Groh (whose Github-repository on latex was the foundation this master's thesis), Leon Duensing, Hannah Van-Santvliet, Pilar Gil Fernández, Isabel Schäfer and many others.	
	\item All my friends (and really all of them) and family from Trieste, in particular my grandparents, who always pushed me on.
\end{itemize}
If I forgot some people, I want to say to them: forgive me, even if you did not end up on this sheet of paper, you have a special place in my heart! 